### 2018-03-12 paper/7-related.tex
Add labels and a TODO for free constructions

\subsection{Other Build Systems}

@@

\subsection{Memoization}

@@

\subsection{Profunctor Optics}

@@

\begin{minted}{haskell}
type Optic c k v = @\std{forall}@ f. c f => (k -> f v) -> k -> f v
\end{minted}

The properties of such optics are well studied, and the functions like \hs{getDependencies} are very much based on observations from that field of work. Alas, we have been unable to remove the \hs{Maybe} used to encode whether a file is an input, without complicating other aspects of our definition. Furthermore, the \hs{Build} operation lacks any further such symmetry.

>>>>

\subsection{Other Build Systems}\label{sec-related-build}

@@

\subsection{Memoization}\label{sec-related-memo}

@@

\subsection{Profunctor Optics}\label{sec-related-optics}

@@

\begin{minted}{haskell}
type Optic p a b s t = p a b -> p s t
\end{minted}

Assuming we instantiate \hs{p} to something that provides \hs{k -> f v} -- which many of the actual instances in that paper do. The properties of such optics are well studied, and the functions like \hs{getDependencies} are very much based on observations from that field of work. Alas, we have been unable to remove the \hs{Maybe} used to encode whether a file is an input, without complicating other aspects of our definition. Furthermore, the \hs{Build} operation lacks any further such symmetry.

\subsection{Free applicative functors and monads}\label{sec-related-free}

\todo{AM}{Mention that one could have chosen a free construction to create
a small DSL for build tasks. Although this simplifies some of the presented
combinators, in general this seems unnecessary.}
